Deep Reinforcement Learning for Conservation Decisions

### 2022-05-28 manuscript/revision_response.Rmd
Small updates

It is possible to use techniques from supervised learning and unsupervised learning in RL. Two examples that come to mind are behavior cloning and “CURL: Contrastive Unsupervised Representations for Reinforcement Learning” by Srinivas et al. Reinforcement learning is a sprawling discipline and since this is an introductory piece where we don’t want to overwhelm the reader, we think it is better to focus on more commonly encountered subjects in the field.

This is a good point that we have attempted to clarify in the manuscript:

@@

We’ve updated this statement as we have found a few noteworthy applications in ecology. Cite !!line!!.

@@

We have put a lot of thought into the topics of evaluating large ML models and ML. We believe the difficulty to evaluate and interpret ML models will be a significant obstacle to RL’s adoption. For large observation-action spaces, there are no available tools that will let you interpret the model, so practitioners must carry out extensive testing to gain confidence in the agent; but, extensive testing for non-tabular observation-action space is still no guarantee that the agent won’t commit undesirable actions. We provided a slight update to a sentence to address these points:

@@

!!Return to this!!

@@

 Identifying under-explored spaces of observation-action is going to be very dependent on the problem. As the observation-action spaces become large, identifying under-explored regions becomes particularly tough. When the observation-action space can easily visualized, then one can use their domain knowledge to improve exploration by say changing the exploration algorithm or tuning the hyperparameters relevant to exploration.

@@

!!We Probably want to make some edits on this point!!

There are two primary ways that one could use domain knowledge to assist the agent in the learning process. One approach is to use a model-based agent where you would instill domain knowledge into the agent’s model of the environment directly. For instance, instead of fitting a neural network to the the transition dynamics, the agent could estimate parameters for a pre-specified model. The benefit of this approach is that the agent could converge to an optimal solution more quickly as the policy search space would be much smaller — note that this benefit would only be true with on-policy algorithms. Another method is to design an exploration algorithm based off of domain knowledge so the agent can more efficiently find good solutions. For both cases, the primary benefit is the same: using domain knowledge can lead to more efficient exploration. Yet, if the domain knowledge is biased, then it is very likely that the agent will learn suboptimal solutions. For instance, with model-based exploration, the agent might spend too much time exploring a low reward region of the observation-action space.

The reviewer here raises a very good point here about employing domain knowledge to reduce computational costs. Certainly, there will be occasions when model-based approaches will outperform model-free methods, and the most significant use case of model-based algorithms is for problems that are computationally expensive.

@@

In other words, the action space can be tailored to fit virtually any decision-making problem. The other question that we interpret this comment to be presenting is whether we can describe all ecological processes mathematically. This is a fundamental philosophy of science question, and is outside of the scope of this paper.

@@

We share this perspective with the reviewer that our study does not prove that deep RL can be immediately applied to conservation problems. This is not the intention of our paper. Instead, we intend our paper to be an introduction for ecologists to deep RL, whereby we introduce the OpenAI Gym framework, some terminology and example problems, so that researchers can investigate deep RL on their own and also better understand how it is beginning to be applied to ecology already. We are at a point in time where researchers and organizations are using deep RL in conservation contexts, so it is imperative for our community to start understanding the benefits and downfalls of using deep RL for our specialized class of problems.

@@

Rescaling does not affect the dynamics. This is equivalent to measuring the process in different units.

>>>>

It is possible to use techniques from supervised learning and unsupervised learning in RL. Two examples that come to mind are behavior cloning and “CURL: Contrastive Unsupervised Representations for Reinforcement Learning” by Srinivas et al. Reinforcement learning is a sprawling discipline, and since this is an introductory piece, we don’t want to overwhelm the reader with the multitude of available approaches. We have tried to focus on the more commonly encountered subjects in the field.

How neural networks can be used is a point that we have attempted to clarify in the manuscript:

@@

We’ve updated this statement as we have found a few note-worthy applications in ecology. Cite !!line!!.

@@

The difficulty around evaluating and interpreting ML models will be a significant obstacle to RL’s adoption on safety-critical problems. For large observation-action spaces, there are no general tools that will let you interpret the model, so practitioners must carry out extensive testing to gain confidence in the agent; but, extensive testing for large (aka non-tabular) observation-action spaces will not guarantee that the agent won’t commit undesirable actions on untested situations. We provided a small update to address these points:

@@

We have updated our description of the discount factor in the manuscript to address these questions:

"a discount factor which describes how much the agent will value rewards to be received in the distant future versus the immediate future"

The exponentiation based on time, t, follows from this description. Since the discount factor is defined on the range (0, 1), the reward will become smaller over the episode. In our problems, we evaluate with a discount factor of 1. It is common however to train the agent with a different discount factor than is used during evaluation, as it may aid exploration to use a different discount factor; thus it is treated like a hyperparameter. The horizon is another phrase for the length of an episode. It is a parameter of the POMDP and not a hyperparameter.

@@

Identifying under-explored spaces of the observation-action space is going to be very dependent on the problem. Usually RL practitioners identify under-explored scenarios by either doing extensive testing or visualizing the policy. As the observation-action spaces become large, identifying under-explored regions becomes particularly tough, since it becomes impossible to visualize the policy. When the observation-action space can be easily visualized, then one can rely on their domain knowledge to recognize sub-optimal performance, which is what we have done in both our examples. So the main recommendation is to first try to visualize the policy then second perform extensive testing to identify areas of poor explorations.

@@

There are two primary ways that one could use domain knowledge to assist the agent in the learning process. One approach is to use a model-based agent where the RL practitioner would instill domain knowledge into the agent’s model of the environment directly. For instance, instead of fitting a randomized neural network to the the transition dynamics, the agent could estimate parameters for a pre-specified model. The benefit of this approach is that the agent could converge to an optimal solution more quickly as the policy search space could be made much smaller for restrictive models — note that this benefit could only be realized with on-policy algorithms, algorithms that explore according to the same policy that they are updating. Another method is to design an exploration algorithm based off of domain knowledge so the agent can more efficiently find good solutions. For both cases, the primary benefit is the same: using domain knowledge can lead to more efficient exploration. Yet, if the domain knowledge is biased, then it is very likely that the agent will learn suboptimal solutions. For instance, with model-based exploration, the agent might spend too much time exploring a low reward region of the observation-action space.

The reviewer here raises a very good point here about employing domain knowledge to reduce computational costs. This is something that we alluded to but did not unpack,

"Fully detailed conservation decision-making problems will likely require comparable specialized algorithms and hardware that ecologists do not generally have access to."

@@

In other words, the action space can be tailored to fit virtually any decision-making problem. The other question that we interpret this comment to be presenting is whether we can describe all ecological processes mathematically. This is a fundamental philosophy of science question that is outside of the scope of this paper.

@@

We share this perspective with the reviewer that our study does not prove that deep RL can be immediately applied to conservation problems. Validating RL as method for ecological problems is not the intention of our paper. Instead, we have written our paper to be an introduction for ecologists to deep RL, whereby we introduce the OpenAI Gym framework, some fundamental RL concepts and example problems, so that researchers can investigate deep RL on their own and better understand how it is beginning to be applied to ecology. We are at a point in time where researchers and organizations are using deep RL in conservation contexts, so it is imperative for our community to start understanding the benefits and downfalls of using deep RL for our specialized class of problems.

@@

Re-scaling the state space is equivalent to measuring the process in different units, so this does not affect the transition dynamics.
